---
output:
  html_document:
    toc: true
    toc_float: true
    css: report.css
params:
  model: model
  type: type
  folder: folder
  plot_folder: plot_folder
  test: test
  response_curves: false
  only_presence: false
  jk: false
  env: null
  clamp: true
  permut: 10
  verbose: true
title: "`r class(params$model@models[[1]])` model for *`r params$model@data@species`*"
---

```{r setup, echo=F, message=FALSE}
options(crayon.enabled = TRUE)
```

**`r class(params$model@models[[1]])`** output produced using **SDMtune** version `r packageVersion("SDMtune")` (Vignali S. *et al.*, 2020).

```{r save files, echo=FALSE, message=FALSE}
if (params$verbose) {
        cli::cli_text("\n")
        cli::cli_progress_step("Save files")
    }
    saveRDS(params$model, file = file.path(params$folder, "model.Rds"))
    swd2csv(params$model@data, file.path(params$folder, "train.csv"))
    if (!is.null(params$test)) 
        swd2csv(params$test, file.path(params$folder, "test.csv"))
```

# ROC curve

```{r plot ROC, echo=FALSE, message=FALSE}
    if (params$verbose)
        cli::cli_progress_step("Plot ROC curve")
    plot <- plotROC_kfold(params$model, test = params$test, show_folds = TRUE)
    suppressMessages(ggplot2::ggsave(filename = "ROC_curve.png", 
        plot = plot, device = "png", path = params$plot_folder))
    path <- file.path(params$plot_folder, "ROC_curve.png")
    element <- stringr::str_glue("\n    <a href='{path}'>\n      <img src='{path}' class='fig-centered'>\n    </a>\n  ")
    htmltools::HTML(element)

```

# Thresholds

```{r thresholds, echo=FALSE, message=FALSE}
if (params$verbose) 
        cli::cli_progress_step("Compute thresholds")

ths <- list()
for (i in 1:4) {
  ths[[i]] <- SDMtune::thresholds(params$model@models[[i]], 
        type = params$type, test = params$test)
}

id_col <- ths[[1]][, 1, drop = FALSE]

numeric_matrices <- lapply(ths, function(df) {
  as.matrix(df[, -1]) |> apply(2, as.numeric)
})

numeric_mean <- Reduce("+", numeric_matrices) / length(numeric_matrices)
ths_mean <- data.frame(id_col, numeric_mean, check.names = FALSE)
ths_PA <- ths_mean[3, 2]


kableExtra::kable_styling(knitr::kable(ths_mean, digits = 20), 
bootstrap_options = c("striped", "hover", "condensed", 
"responsive"))

```

`r if(!params$response_curves) {"<!--"}`
# Response curves {#response}

### Marginal curves:

```{r marginal response, message=FALSE, echo=FALSE, warning=FALSE, eval=params$response_curves}
type <- "marginal"
if (params$verbose) 
        cli::cli_progress_step("Plot {type} response curves")
    vars <- sort(colnames(params$model@data@data))
    elements <- c()
    for (var in vars) {
        plot <- plotResponse(params$model, var, type = params$type, 
            only_presence = params$only_presence, marginal = ifelse(type == 
                "marginal", TRUE, FALSE), rug = TRUE, color = "#4bc0c0")
        fname <- paste0(var, "_", type, ".png")
        suppressMessages(ggplot2::ggsave(filename = fname, plot = plot, 
            device = "png", path = params$plot_folder))
        path <- file.path(params$plot_folder, fname)
        element <- stringr::str_glue("\n      <a href='{path}'>\n        <figure title='{var}'>\n          <img src='{path}'>\n          <figcaption>{var}</figcaption>\n        </figure>\n      </a>\n    ")
        elements <- c(elements, element)
    }
    elements <- paste(c(elements, "<p></p>"), collapse = "")
    htmltools::HTML(elements)
```

### Univariate curves:

```{r univariate response, message=FALSE, echo=FALSE, warning=FALSE, eval=params$response_curves}
 type <- "univariate"
if (params$verbose) 
        cli::cli_progress_step("Plot {type} response curves")
    vars <- sort(colnames(params$model@data@data))
    elements <- c()
    for (var in vars) {
        plot <- plotResponse(params$model, var, type = params$type, 
            only_presence = params$only_presence, marginal = ifelse(type == 
                "marginal", TRUE, FALSE), rug = TRUE, color = "#4bc0c0")
        fname <- paste0(var, "_", type, ".png")
        suppressMessages(ggplot2::ggsave(filename = fname, plot = plot, 
            device = "png", path = params$plot_folder))
        path <- file.path(params$plot_folder, fname)
        element <- stringr::str_glue("\n      <a href='{path}'>\n        <figure title='{var}'>\n          <img src='{path}'>\n          <figcaption>{var}</figcaption>\n        </figure>\n      </a>\n    ")
        elements <- c(elements, element)
    }
    elements <- paste(c(elements, "<p></p>"), collapse = "")
    htmltools::HTML(elements)
```

`r if(!params$response_curves) {"-->"}`

`r if(is.null(params$env)) {"<!--"}`
# Distribution map

```{r prediction, echo=FALSE, message=FALSE, eval=!is.null(env)}
#.make_report_prediction(params)
 if (params$verbose) 
        cli::cli_progress_step("Predict distribution map")
    pred <- predict(params$model, data = params$env, type = params$type, fun = c("mean", "sd", "max", "min", "median"), filename = file.path(params$plot_folder, "map.tif"), overwrite = TRUE, clamp = params$clamp, format = "GTiff")
      plot <- plotPred(pred$mean, lt = params$type, hr = TRUE, colorramp = c("#2c7bb6", 
        "#abd9e9", "#ffffbf", "#fdae61", "#d7191c"))
    suppressMessages(ggplot2::ggsave(filename = "map_mean.png", plot = plot, 
        device = "png", path = params$plot_folder))
    path <- file.path(params$plot_folder, "map_mean.png")
    element <- stringr::str_glue("\n    <a href='{path}'>\n      <img src='{path}' class='fig-centered'>\n    </a>\n  ")
    htmltools::HTML(element)
```


# SD map

```{r prediction SD, echo=FALSE, message=FALSE, eval=!is.null(env)}
 if (params$verbose) 
        cli::cli_progress_step("Predict SD distribution map")
    plot <- plotPred(pred$sd, lt = params$type, hr = TRUE, colorramp = c("#2c7bb6", 
        "#abd9e9", "#ffffbf", "#fdae61", "#d7191c"))
    suppressMessages(ggplot2::ggsave(filename = "map_sd.png", plot = plot, 
        device = "png", path = params$plot_folder))
    path <- file.path(params$plot_folder, "map_sd.png")
    element <- stringr::str_glue("\n    <a href='{path}'>\n      <img src='{path}' class='fig-centered'>\n    </a>\n  ")
    htmltools::HTML(element)
```


`r if(is.null(params$env)) {"-->"}`

# Variable importance

```{r variable importance, echo=FALSE, message=FALSE}
if (params$verbose) 
        cli::cli_progress_step("Compute variable importance")
    kableExtra::kable_styling(knitr::kable(varImp(params$model, 
        params$permut, progress = FALSE)), bootstrap_options = c("striped", 
        "hover", "condensed", "responsive"), full_width = FALSE)
```

`r if(!params$jk) {"<!--"}`
# Jackknife test

```{r, echo=FALSE, message=FALSE, eval=params$jk}
.compute_report_jk(params, test)
```

`r if(!params$jk) {"-->"}`

# References

- Vignali, S., Barras, A. G., Arlettaz, R., Braunisch, V. (2020). *SDMtune*: An R package to tune and evaluate species distribution models. Ecology and Evolution, **10**(20), 11488–11506. <https://doi.org/10.1002/ece3.6786>
- Vignali, S., Barras, A. G., Braunisch, V. (`r format(packageDate("SDMtune"), format = "%Y")`). *SDMtune*: Species Distribution Model Selection. R package version `r packageVersion("SDMtune")`. `r ifelse(grepl("9000",packageVersion("SDMtune")), "<https://github.com/ConsBiol-unibern/SDMtune>", "<https://CRAN.R-project.org/package=SDMtune>")`
